Using Stochastic Modeling to Predict Long Timescale Transport Behavior of Solutes in an H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-06-25 Ben_Manuscripts/transport/response_to_reviewers.tex

    \item \begin{quote}
    \textit{The explanation regarding the transport of water molecules in the tail 
    region relative to water molecules in the pore region for the 5\% (by weight) 
    water system that occurs in the paragraph that begins at the end of page 20 is
    rather unsatisfying. While certain statistics are pointed to, there is not a 
    full explanation provided here. Expanding this point in order would strengthen
    the manuscript.}
    \end{quote}

    Author reply: We thank the reviewer for pushing us to strengthen our description
    of tail water transport in the 5 wt\% water system, as our point could be 
    confusing without proper explanation.

    Original text: ``This anomaly is likely a consequence of lower density in the
    distal tails relative to the pores, leading to faster diffusion in the tails,
    as well as slowed diffusion of water molecules in the pores via hydrogen 
    bonds with other water molecules and association with sodium ions. Water molecules are 
    less likely to hydrogen bond with each other while in the distal tail region since they
    are interspersed between chains, while those in the pores stay in close proximity to 
    each other. We observed about 9 times more hydrogen bonding between water molecules 
    near the pore center versus those in the distal tail region. Additionally, an average 
    of 65\% of water molecules in the pores of the 5 wt\% water system are associated
    with a sodium ion each frame compared to 44\% in the 10 wt\% water system. There is a
    negligible amount of hydrogen bonds between water molecules and monomer head groups.

    New text: ``This behavior is likely due to the
    much more crowded pore environment in the 5 wt\% versus the 10 wt\% water system. 
    Monomer head groups are concentrated about 2~\AA~closer to the pore centers in the
    5 wt\% versus the 10 wt\% water system (see Figure~\ref{M-fig:component_densities})
    which leaves less space for water molecules and restricts their movement among the 
    relatively immobile monomer head groups. The consequently high energetic barrier 
    to diffusion enhances the favorability of associative interactions between water
    and monomer components. The 95th percentile lifetime of hydrogen bonds between 
    water molecules located near the pore center is 2.1 ns in the 5 wt\% system compared
    to 0.5 ns in the 10 wt\% system. However, since we only saved simulation output 
    every 0.5 ns, it is likely that the true hydrogen bond lifetimes in the 10 wt\% 
    system are shorter than this value. Additionally, there are more frequent and longer
    periods of association between water and sodium ions. An average of 65\% of water 
    molecules in the pores of the 5 wt\% water system associate with a sodium ion each
    frame compared to 44\% in the 10 wt\% water system. There are about half as many water
    molecules in the 5 wt\% water system which allows a larger fraction of them to 
    associate with sodium ions. The lifetime of associations between sodium ions and 
    water is 7.5 ns and 3.0 ns in 5 and 10 wt\% water systems respectively.``

@@

	\end{quote}

	Author reply: We thank the reviewer for pointing out that we are missing this essential detail.
	We have added the following text to section 2.1 of the main text:

	New text: ``We simulated water molecules using the TIP3P water model because it is
	the water model that GAFF and other AMBER family parameters have been optimized
    with.''
%    computationally efficient and reasonably reproduces water's physical properties
%    at 300K, the temperature of our simulations.``

    %MRS: TIP-4P is pretty close in efficiency, and TIP3P is only mediocre in bulk water properties  I would probably say that TIP3P was used because it is the water model that GAFF and other AMBER family parameters were optimized with.  TIP3P also diffuses faster than experimental water, which is both a negative (can't compare absolute diffusion) and positive (things happen faster). 
    %BJC2: I don't see any mention of water models in the GAFF paper. Maybe I'm overlooking something. 
    % Instead, I cited a study of TIP3P in a lipid membrane system where the lipids were parameterized with
    % GAFF.
    %MRS: Gaff uses the same charge model and VDW types that AMBER does, which was parameterized to be compatible with TIP3P water.

@@

    \textit{I think most of the text related to preparation of the model systems (Section S2, 
    Supporting Information), should be moved into the Methods section of the paper. I believe 
    these simulation setup details are important to researchers working with somewhat similar 
    systems.}

    \end{quote}

    Author reply: We thank the reviewer for their suggestion. We've edited Section 2.2 of the main
    text to include a consolidated discussion of the data and analysis presented in Section S2, 
    while leaving the full discussion in Section S2.

    Old text: ``We observed that some water partitions into the distal tail region of our system and therefore
	built our initial configurations with water in both regions, close to the expected
	equilibrium partition (see Section~\ref{S-section:water_content_equil} of the Supporting
	Information). We define the distal tail region to be ca. 1.5 nm from the pore
	center based on the minimum in the radial distribution function of water
	(see Section~\ref{M-method:rdfs}). The amount of water present in the distal tail region
	may or may not be experimentally consistent but it is necessary for our results to be 
	thermodynamically consistent; otherwise, water would slowly leak from the pore into the
	tail region over several hundred nanoseconds. We iteratively adjusted the pore radius in our systems
	until the appropriate amount of water fit in the pores after running the GROMACS command
	\texttt{gmx solvate}. We placed water molecules in the distal tail region one at a time
	in random locations with a short energy minimization between each insertion. When 
	studying transport of water in the pores, we limited the calculations to water molecules
	that spent greater than 95\% of their time outside of the distal tail region. We 
	justify this decision with better context in Section~\ref{M-section:transport_water_sodium}.

### 2019-07-27 Ben_Manuscripts/stochastic_transport/Outline.tex
Incorporating iHMM

%BJC: potential titles (uncommented is current favorite)
%\title{The Transport Mechanisms of Polar Solutes in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\title{Size, Shape and Functionality Dependence of Solute Transport Mechanisms in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

  Unfortunately, the timescales that we can simulate with MD are insufficient to be
  able to predict macroscopic transport properties traditionally used to characterize
  membranes in the lab.

@@

  In this work, we have determined the transport mechanisms and macroscopic
  transport properties exhibited by a number of polar solutes with varying size,
  chemical functionality and hydrophilic character.
  \begin{itemize}
	\item Many of the separations we are interested in involve polar organic 
	compounds.
  \end{itemize}

  We have compared our calculated diffusion coefficients with experimental
  measurements made using DOSY NMR.

@@

@@

  \subsubsection*{System Setup}

  There is a broad range of water concentrations which will form a stable 
  H\textsubscript{II} phase with Na-GA3C11. 
  \begin{itemize}
	\item In the literature this system is typically synthesized with close
	to 10 wt \% water
    \item However, Resel et al. noted that the system is likely fully 
	hydrated with less than 7 wt \% water.
	\item We decided to test two different levels of water content: 5 and 10 wt \%
  \end{itemize}

  We observed that water partitions into the tail region of our system and therefore
  built our initial configurations with water in both regions close to the expected
  equilibrium value.
  \begin{itemize}
	\item There is about 2:1 water in the pores versus in the tails for the 10 wt \% system.
	\item The amount of water present in the tails may or may not be experimentally consistent
	but if we don't put it in, the results will not be thermodynamically consistent, which 
	will give issues with measurements and calculations.
	\item See supporting info for water equilibration simulation data.
	\item We adjusted the pore radius in our systems so that the right amount of water
	fits in the pores without any vacuum using \texttt{gmx solvate}.
	\item We placed water molecules in the tail region one at a time in random locations
	with short energy minimizations between insertions.
  \end{itemize}

%  We equilibrated the initial configuration using the `wet' equilibration procedure
%  described in our previous work (reference to structure paper).
  %BJC: not sure I need to go into any details describing that procedure
%  \begin{itemize}
%	\item Series of NVT simulations with force constants on carbon atoms of aromatic
%	ring in head group
%	\item Force constants reduced according to the sequence: 1000000, 3162,
%	56, 8, 3, 2, 1, 0 kJ mol$^{-1}$ nm$^{-2}$ 
%  \end{itemize}

%  We cross-linked the equilibrated solvated configuration using the cross-linking procedure
%  described in our previous work.

  We equilibrated an initial solvated configuration before adding solutes.
  \begin{itemize}
	\item We equilibrated the initial configuration using the `wet'
	equilibration procedure described in our previous work~\cite{coscia_understanding_2019}.
	\item We cross-linked the equilibrated solvated configuration using the
	cross-linking procedure described in our previous work. 
  \end{itemize}

  We added 6 solute molecules to each pore of the equilibrated cross-linked
  configuration.
  \begin{itemize}
	\item We equally spaced each solute in the pore
	\item 6 solutes per pore provided a balance of a useful amount of data
	for generating statistics and a low degree of interaction between solutes (reference
	to supporting information to show low degree of interaction)
	\item At each insertion point we placed a randomly oriented solute molecule
	then ran a short energy minimzation.
	\item We allowed the solutes to equilibrate for 5 ns using berendsen 
	pressure control
	\item We collected transport data using long simulations, on the order of
	1 microsecond
	\item .mdp files are in the supporting information % with pressure controlled by the Parrinello-Rahman barostat.
  \end{itemize}

  \subsubsection*{Modeling subdiffusion}\label{method:model_sFBM}

  Solutes in our H\textsubscript{II} LLC membrane exhibit subdiffusive
  behavior, a type of anomalous diffusion. 
  \begin{itemize}
  	\item During an anomalous diffusion process, the mean squared displacement (MSD)
  	does not grow linearly with time, rather it is of the form:
	\begin{equation} 
	\langle x^2(t) \rangle = K_{\alpha}t^\alpha
	\label{eqn:msd_form}
	\end{equation} 
	where $\alpha$ is the anomalous exponent and $K_\alpha$ is the
	generalized diffusion coefficient.
	\item A value of $\alpha < 1$ indicates a subdiffusive process, while a value of
	$\alpha = 1$ and $\alpha > 0$ is characteristic of Brownian and superdiffusive
	motion respectively.
  \end{itemize}

  \noindent We calculated both the ensemble-averaged and time-averaged MSDs
  of the simulated trajectories.
  \begin{itemize}
	\item The ensemble-averaged MSD measures the displacement of a particle from its initial
	position~\cite{meroz_toolbox_2015} and can be written as
	\begin{equation}
	\langle x^2(t) \rangle = \langle x(t) - x(0) \rangle
	\label{eqn:ensemble_msd}
	\end{equation}
%	\item The average MSD calculated in this way recovers the form of
%	Equation~\ref{eqn:msd_form}. % time-averaged should recover it too for FBM 
	\item The time-averaged MSD measures the displacement between all possible time lags
	and can be written as
	\begin{equation}
	\overline{x^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (x(t + \tau) - x(t))^2 dt
	\end{equation}
	where $\tau$ is the time lag and T is the length of the
	trajectory~\cite{meroz_toolbox_2015}. 
%	\item The time-averaged MSD becomes linear in our simulations,
%	therefore we can fit a line to its slope in order to estimate the macroscopic
%	diffusivity of the particle.
	%BJC: this needs more justification. Not many people have done it
	%BJC: could also not report them as diffusivities. Comparison of total MSD
	% should give same information
	% Linear region probably exists because dwell times on the order of large lag times
	% become negligible
  \end{itemize}

@@

  \noindent We believe that solutes in the system studied here exhibit subordinated 
  fractional Brownian motion (sFBM) where the parent process is FBM and the 
  leading process is a CTRW. 
  \begin{itemize}
  	\item The ensemble-averaged MSD differs from the time-averaged MSD, which
  	is indicative of non-ergodicity, a trait inherent to CTRWs but not FBM or RWFs.~\cite{thiel_weak_2014}
  	\item We also observe non-stationary $z$-coordinate traces of each solute's
  	center of mass (COM). %BJC: figure of a z-coordinate trace in main text or in supporting info
  	\item For a pure CTRW, the time-averaged MSD should be linear.
  	~\cite{neusius_subdiffusion_2008,meroz_subdiffusion_2010}
  	\item However, a typical time-averaged solute MSD is sublinear (see supporting
  	information), which suggests that there is another underlying subdiffusive mechanism.
  	\item The hop lengths recorded after each dwell period are anti-correlated (See supporting information)
  	\item Given the viscoelastic nature of the monomers in our system, we believe
  	the hop lengths can be modeled with FBM. 
 	\item For subordinated FBM, it can be shown that
  	\begin{equation}
  	\langle x^2(t) \rangle \simeq t^{\alpha\beta}
  	\end{equation}
  	where $\alpha$ is the anomalous exponent characteristic of the leading CTRW process
  	and $\beta$ is the anomalous exponent characteristic of the parent FBM process. 
  \end{itemize}

  \noindent We can characterize a CTRW process using the parameters which describe its
  dwell time and hop length distribution.
  \begin{itemize}
	\item We used the \texttt{ruptures} python package in order to identify
	breakpoints in solute trajectories.\cite{truong_ruptures:_2018} (See Supporting Information for more
	details on chosen parameters. i.e. type of cost function, cost function penalty
	tolerance, number of dimensions used)
	\item The corresponding hop lengths and dwell times between break points were 
	used to construct empirical distributions.
	\item For solutes in our system, the distribution of hop lengths is
	well-represented by a Gaussian distribution.~\cite{metzler_random_2000,
	metzler_anomalous_2014,neusius_subdiffusion_2009}
	\item We are most interested in the standard deviation, $\sigma$, of the 
	hop length distribution.
	\item The distribution of dwell	times is expected to fit a power law (or heavy-tailed)
	distribution proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
	\item Because we are limited to taking measurements at discrete values
	dictated by the output frequency of our simulation trajectories, we fit the
	empirical dwell times to a discrete power law distribution whose maximum
	likelihood $\alpha$ parameter we calculated by maximizing the following
	likelihood function: 
        \begin{equation}
	\mathcal{L}(\beta) = -n\text{ln}\zeta(\beta, x_{min}) -
	\beta\sum_{i=1}^{n} \text{ln}~x_i 
	\label{eqn:powerlaw_likelihood}
	\end{equation}
	where $\beta = 1 + \alpha$, $x_i$ are collected dwell time data points,
	$n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
	where $x_{min}$ is the smallest measured value of
	$x_i$.~\cite{clauset_power-law_2009} 
	\item We obtained distributions of the hop length standard deviations, $\sigma$, and
	$\alpha$ using statistical bootstrapping.\cite{efron_introduction_1994} 
  \end{itemize}

@@

@@

%  We calculated macroscopic diffusion coefficients by simulating trajectories orders of
%  magnitude longer than our molecular simulations.
  \noindent For each solute, we simulated 10000 sFBM trajectories for 1 $\mu$s each. 
  \begin{itemize}
	\item We constructed trajectories by simulating	sequences of dwell times and correlated 
	hop	lengths generated based on parameters randomly chosen from our bootstrapped parameter
	distributions.
	\item We propagated each trajectory until the total time reached 1 $\mu$s, and truncated
	the last data point so that the total time exactly equaled 1 $\mu$s. 
    \item Valid comparisons are only possible between fixed length sFBM simulations. The
    power law dwell time behavior gives rise to the aging phenomenon, embodied by
    a decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
    \item We reported the MSD after 1 $\mu$s with corresponding 95 \% intervals
% Following probably better suited for supporting information, if included at all
%	\item We randomly sample Gaussian hop lengths using the
%	\texttt{numpy.random.normal} method of the \texttt{numpy} python package.
%	\item We randomly sampled dwell times from a discrete power law
%	distribution based on the recommendations of Clauset et
%	al.~\cite{clauset_power-law_2009}: 
%	\begin{equation}
%	x = \lfloor
%	(x_{min} - \tfrac{1}{2})(1 - r)^{-1/(\alpha - 1)} + \tfrac{1}{2} \rfloor
%	\label{eqn:discrete_powerlaw_draws}
%	\end{equation}
%	where $r$ is randomly drawn from a uniform distribution which we simulated
%	with \texttt{numpy.random.uniform}.
%	\item We found that thermal noise does not significantly influence the MSD and
%	therefore did not add any noise to the simulated trajectories. (See supporting info)
  \end{itemize}

@@

  \subsubsection*{Radial Distribution Functions}

  We measured the average radial distance of each solute of interest from the pore
  centers.
  \begin{itemize}
	\item We binned the radial distances and then normalized by the volume
	of the annulus defined by the bin edges.
	\item Although the pores are often described as straight, they have a
	small degree of tortuosity which disrupts the RDF calcuation 
	\item We obtain the best RDF by constructing splines that run through the
	pore centers.
	\item We construct the splines by dividing the membrane into 20 slices
	in the $z$-direction. Within each slice, we calculate the location of 
	the pore centers based on the average location of the aromatic rings
	that make up the monomer head groups.
	\item When calculating the RDF, the radial distance from the pore center
	is based on the distance between the solute center-of-mass and the ($x$, $y$)
	coordinates of appropriate point on the spline.
  \end{itemize}

  \subsubsection*{Coordination number}

  We quantified the coordination of solutes with surrounding molecules.
  \begin{itemize}
  	\item For each frame, we counted the identities and number of
  	coordinated molecules to a given solute based on a distance cut-off. 
	\item We found that this approach is more useful than calculating the
	3D spherical radial distribution function because it gives detailed
	frame-by-frame information rather than an average. 
  \end{itemize}

  \subsection{Experimental}
  % BJC: For Greg to write if things work out

@@

  \end{itemize}

@@

  \bibliographystyle{ieeetr}
  \bibliography{transport}

>>>>

\title{Using Stochastic Modeling to Predict Long Timescale Transport Behavior of Solutes in an H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

  Unfortunately, the timescales that we can simulate with MD are insufficient to be
  able to predict well-converged predictions of macroscopic transport properties 
  traditionally used to characterize membranes in the lab.

@@

  In this work, we explore two approaches to modeling the dynamic behavior of 
  a subset of solutes that we studied in our previous work.
  \begin{itemize}
  	\item First is based on the anomalous diffusion literature
  	\item Our second approach to modeling solute transport groups solute behavior
    into different dynamical states.
%  	\item Second focuses on the analysis of time series  % Need a better way to talk about it here 
  \end{itemize}

@@

  We ran all MD simulations and energy minimizations using GROMACS 2018. We
  performed all post-simulation trajectory using python scripts which are available
  online at \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.

@@

  We studied transport of solutes in the H\textsubscript{II} phase using an
  atomistic molecular model of four pores in a monoclinic unit cell with 
  10 \% water by weight. 
  \begin{itemize}
    \item Approximately one third of the water molecules occupy the tail region 
    with the rest near the pore center.
    \item We chose to study the 10 wt \% water system because solutes move 
    significantly faster than in the 5 wt \% system studied previously.
    \item Appropriate stochastic modeling requires that solutes explore 
    as much structural space as possible.  %BJC: better term than structural space?
  \end{itemize}

  We chose to study a subset of 4 of the fastest moving solutes from our previous
  work: methanol, acetic acid, urea and ethylene glycol.
  \begin{itemize} 
    \item In addition to exploring membrane structural space the most, these solutes
    have a relatively diverse set of chemical functionality.   
    \item For each solute we created a separate system and to each system we
    added 6 solutes per pore for a total of 24 solutes.
    \item This number of solutes per pore provides a balance of a low 
    degree of interaction between solutes and sufficient amount of data from
    which to generate statistics on the time scales which we simulate.
    \item Further details on the setup and equilibration of these systems can
    be found in our previous work.\cite{coscia_chemically_2019}
  \end{itemize}

  We extended the 1 $\mu$s simulations of our previous work to 5 $\mu$s in order
  to collect ample data.
  \begin{itemize}
    \item We simulated the system with a time step of 2 fs at a pressure of 1 bar
    and 300 K controlled by the Parinello-Rahman barostat and the v-rescale thermostat
    respectively.
  \end{itemize}

  \subsection{Modeling subdiffusion}\label{method:model_sFBM}

  Solutes in our H\textsubscript{II} LLC membrane system exhibit subdiffusive
  behavior, a type of anomalous diffusion.
  \begin{itemize}
  	\item During an anomalous diffusion process, the mean squared displacement (MSD)
  	does not grow linearly with time, rather it is of the form:
	\begin{equation} 
	\langle x^2(t) \rangle = K_{\alpha}t^\alpha
	\label{eqn:msd_form}
	\end{equation} 
	where $\alpha$ is the anomalous exponent and $K_\alpha$ is the
	generalized diffusion coefficient.
	\item A value of $\alpha < 1$ indicates a subdiffusive process, while values of
	$\alpha = 1$ and $\alpha > 0$ are characteristic of Brownian and superdiffusive
	motion respectively.
  \end{itemize}

  \noindent We analyzed both the ensemble-averaged and time-averaged MSDs
  of the simulated trajectories.
  \begin{itemize}
	\item The ensemble-averaged MSD measures the displacement of a particle from its initial
	position~\cite{meroz_toolbox_2015} and can be written as
	\begin{equation}
	\langle x^2(t) \rangle = \langle x(t) - x(0) \rangle
	\label{eqn:ensemble_msd}
	\end{equation}
%	\item The average MSD calculated in this way recovers the form of
%	Equation~\ref{eqn:msd_form}. % time-averaged should recover it too for FBM 
	\item The time-averaged MSD measures the displacement between all possible time lags
	and can be written as
	\begin{equation}
	\overline{x^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (x(t + \tau) - x(t))^2 dt
	\end{equation}
	where $\tau$ is the time lag and T is the length of the
	trajectory~\cite{meroz_toolbox_2015}. 
  \end{itemize}

@@

  % BJC: Should this be in the results?
  \noindent We believe that solutes in the system studied here exhibit subordinated 
  fractional Brownian motion (sFBM) where the parent process is FBM and the 
  leading process is a CTRW. 
  \begin{itemize}
  	\item The ensemble-averaged MSD differs from the time-averaged MSD, which
  	is indicative of non-ergodicity, a trait inherent to CTRWs but not FBM or RWFs.~\cite{thiel_weak_2014}
  	\item We also observe non-stationary $z$-coordinate traces of each solute's
  	center of mass (COM). %BJC: figure of a z-coordinate trace in main text or in supporting info
  	\item For a pure CTRW, the time-averaged MSD should be linear.
  	~\cite{neusius_subdiffusion_2008,meroz_subdiffusion_2010}
  	\item However, a typical time-averaged solute MSD is sublinear (see supporting
  	information), which suggests that there is another underlying subdiffusive mechanism.
  	\item The hop lengths recorded after each dwell period are anti-correlated (See supporting information)
  	\item Given the viscoelastic nature of the monomers in our system, we believe
  	the hop lengths can be modeled with FBM. 
 	\item For subordinated FBM, it can be shown that
  	\begin{equation}
  	\langle x^2(t) \rangle \simeq t^{\alpha\beta}
  	\end{equation}
  	where $\alpha$ is the anomalous exponent characteristic of the leading CTRW process
  	and $\beta$ is the anomalous exponent characteristic of the parent FBM process. 
  \end{itemize}

  \noindent We can characterize a CTRW process using the parameters which describe its
  dwell time and hop length distribution.
  \begin{itemize}
	\item We used the \texttt{ruptures} python package in order to identify
	changepoints in solute trajectories.\cite{truong_ruptures:_2018} (See Supporting
	Information for more details on chosen parameters. i.e. type of cost function, 
	cost function penalty tolerance, number of dimensions used)
	\item We used the corresponding hop lengths and dwell times between break points
	to construct empirical distributions.
  \end{itemize}

  For solutes in our system, the distribution of hop lengths appears to be
  well-represented by a Gaussian distribution.~\cite{metzler_random_2000,
  metzler_anomalous_2014,neusius_subdiffusion_2009}
  \begin{itemize}
	\item We are most interested in the standard deviation, $\sigma$, of the 
	hop length distribution.
  \end{itemize}

  The distribution of dwell	times is expected to fit a power law (or heavy-tailed)
  distribution proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
  \begin{itemize}
	\item Because we are limited to taking measurements at discrete values
	dictated by the output frequency of our simulation trajectories, we fit the
	empirical dwell times to a discrete power law distribution whose maximum
	likelihood $\alpha$ parameter we calculated by maximizing the following
	likelihood function: 
        \begin{equation}
	\mathcal{L}(\beta) = -n\text{ln}\zeta(\beta, x_{min}) -
	\beta\sum_{i=1}^{n} \text{ln}~x_i 
	\label{eqn:powerlaw_likelihood}
	\end{equation}
	where $\beta = 1 + \alpha$, $x_i$ are collected dwell time data points,
	$n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
	where $x_{min}$ is the smallest measured value of
	$x_i$.~\cite{clauset_power-law_2009} 
	\item We obtained distributions of the hop length standard deviations, $\sigma$, and
	$\alpha$ using statistical bootstrapping.\cite{efron_introduction_1994} 
  \end{itemize}

@@

  In general, we observe different dynamical behavior when solutes move inside the
  pore versus in the tail region.
  \begin{itemize}
    \item Therefore, we created 2 sets of parameters based on the solute's radial location.
    \item Solutes in the pore region are located less than 0.75 nm from the pore center and
    all else are in the tail region. 
    \item We determined this cut-off and described how we calculated radial 
    distance from the pore center in our previous work~\cite{coscia_chemically_2019}
  \end{itemize}

@@

%  We calculated macroscopic diffusion coefficients by simulating trajectories orders of
%  magnitude longer than our molecular simulations.
  \noindent For each solute, we simulated 10000 5 $\mu$s sFBM trajectories. 
  \begin{itemize}
	\item We constructed trajectories by simulating	sequences of dwell times and correlated 
	hop	lengths generated based on parameters randomly chosen from our bootstrapped parameter
	distributions.
	\item We propagated each trajectory until the total time reached 1 $\mu$s, and truncated
	the last data point so that the total time exactly equaled 5 $\mu$s. 
    \item Valid comparisons are only possible between fixed length sFBM simulations. The
    power law dwell time behavior gives rise to the aging phenomenon, embodied by
    a decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
    \item We reported the MSD after 5 $\mu$s with corresponding 95 \% intervals
% Following probably better suited for supporting information, if included at all
%	\item We randomly sample Gaussian hop lengths using the
%	\texttt{numpy.random.normal} method of the \texttt{numpy} python package.
%	\item We randomly sampled dwell times from a discrete power law
%	distribution based on the recommendations of Clauset et
%	al.~\cite{clauset_power-law_2009}: 
%	\begin{equation}
%	x = \lfloor
%	(x_{min} - \tfrac{1}{2})(1 - r)^{-1/(\alpha - 1)} + \tfrac{1}{2} \rfloor
%	\label{eqn:discrete_powerlaw_draws}
%	\end{equation}
%	where $r$ is randomly drawn from a uniform distribution which we simulated
%	with \texttt{numpy.random.uniform}.
%	\item We found that thermal noise does not significantly influence the MSD and
%	therefore did not add any noise to the simulated trajectories. (See supporting info)
  \end{itemize}

@@

%  \subsubsection*{Coordination number}

%  We quantified the coordination of solutes with surrounding molecules.
%  \begin{itemize}
%  	\item For each frame, we counted the identities and number of
%  	coordinated molecules to a given solute based on a distance cut-off. 
%	\item We found that this approach is more useful than calculating the
%	3D spherical radial distribution function because it gives detailed
%	frame-by-frame information rather than an average. 
%  \end{itemize}

  \subsection{The Infinite State Hidden Markov Model}

  Hidden Markov models (HMMs) are a useful and widely used technique
  for modeling sequences of observations where the probability of the next observation
  in a sequence depends only on a previous unobserved, or hidden, state.~\cite{beal_infinite_2002}
  \begin{itemize}
    \item In the context of our simulations, the observations correspond to 
    the center of mass coordinates of the solutes versus time, and the states
    correspond to the dynamical behavior which giving rise to those types
    of observations.
    \item Unfortunately, HMMs require the number of hidden states to be known
    a priori.
  \end{itemize}

  The infinite-state HMM overcomes this drawback using a hierarchical
  Dirichlet process (HDP).
  \begin{itemize}
    \item Using some base probability distribution, H, a Dirichlet process 
    (DP) generates distributions over a countably infinite number of 
    probability measures:
    \begin{equation}
      G_0 = \sum_{k=1}^{\infty} \beta_k \delta_{\theta_k} ~~ \theta_k \sim H
    \end{equation}
  \end{itemize}

@@

@@

  \bibliographystyle{ieeetr}
  \bibliography{stochastic_transport}
